How has the Amazon been construed as a problem? Preliminary Analysis

### 2022-04-07 Draft_April_2022/Full_draft_20220401.rmd
#figure1 w/ controlled line

```{r Amazonian speeches by year, echo=FALSE, message=FALSE, warning=TRUE, paged.print=TRUE, include=TRUE}
perc1 <- pop %>%
  count(amazon_speech, year)%>%
  group_by(year)%>%
  mutate(perc=n / sum(n)) %>%
  select(c(perc,amazon_speech, year))
Amazon_year <- pop %>%
  count(amazon_speech, year) %>%
  group_by(year) %>%
  left_join(perc1) %>%
  filter(amazon_speech==1) %>%
  ggplot(., aes(x = year, y = perc)) +
  geom_line(color="darkolivegreen")+
  scale_y_continuous(labels = percent_format())+
  scale_fill_brewer(type = "qual", palette = "Set2", direction= -1)+
  labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
       subtitle = "Sample composed by 6130 presidential speeches since 1985", caption = "") +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "right")
Amazon_year
```

>>>>

```{r Amazonian speeches by year, echo=FALSE, message=FALSE, warning=TRUE, paged.print=TRUE, include=TRUE}

pop2 <- pop %>% count(amazon_speech, year, president) %>%
  group_by(year, president) %>%
  left_join(perc1) %>%
  filter(amazon_speech==1)

  pop2 <- left_join(pop2, AAI, by = "year")
  pop2 <- left_join(pop2, amazon_def_year, by = "year")

model <- lm(perc ~ AAI+ def_year + president, data=pop2)

pop2$predicted = predict(model, pop2)

Amazon_year <- pop2 %>% ggplot(., aes(x = year, y = perc)) +
  geom_line(size=.85, aes(x=year, y=perc, color="Real share"))+
  geom_line(size=.45, aes(x=year, y=predicted, color= "Predicted share"))+
  scale_color_manual(values=c("Real share"="darkolivegreen", "Predicted share"= "gray40"))+
  scale_y_continuous(labels = percent_format())+
  labs(
    x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
    subtitle = "Sample composed by 6130 presidential speeches since 1985",
    caption = "Predicted share controls for deforestation rates, inflation, and president.", color='Y series') +
  theme(
    panel.background = element_rect("white", "black", .5, "solid"),
    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
    axis.text = element_text(color = "black", size = 10),
    title = element_text(color = "black", size = 10, face = "bold"),
    legend.title = element_blank(),
    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
    legend.position = "bottom"
  )

Amazon_year
```

### 2022-04-07 analysis/analysis_livio.Rmd
#figure1 w/ controlled line

amazon_def_year <- mutate(amazon_def_year, year = year + 1) %>%
  rename(def_year = "area km\u00b2")

@@

>>>>

AAI <- readRDS("~/Documents/GitHub/amazondef/data/AAI.Rds")

@@

```{r Amazonian speeches by year III, echo=FALSE, message=FALSE, warning=TRUE, echo=FALSE, paged.print=TRUE}

pop2 <- pop %>% count(amazon_speech, year, president) %>%
  group_by(year, president) %>%
  left_join(perc1) %>%
  filter(amazon_speech==1)

  pop2 <- left_join(pop2, AAI, by = "year")
  pop2 <- left_join(pop2, amazon_def_year, by = "year")

model <- lm(perc ~ AAI+ def_year + president, data=pop2)

pop2$predicted = predict(model, pop2)

pop2 %>% ggplot(., aes(x = year, y = perc)) +
  geom_line(size=.85, aes(x=year, y=perc, color="Real share"))+
  geom_line(size=.45, aes(x=year, y=predicted, color= "Predicted share"))+
  scale_color_manual(values=c("Real share"="darkolivegreen", "Predicted share"= "gray40"))+
  scale_y_continuous(labels = percent_format())+
  labs(
    x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
    subtitle = "Sample composed by 6130 presidential speeches since 1985",
    caption = "Predicted share controls for deforestation rates, inflation, and president.", color='Y series') +
  theme(
    panel.background = element_rect("white", "black", .5, "solid"),
    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
    axis.text = element_text(color = "black", size = 10),
    title = element_text(color = "black", size = 10, face = "bold"),
    legend.title = element_blank(),
    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
    legend.position = "bottom"
  )
